---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# jikanr

<!-- badges: start -->
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

## Overview

jikanr is a R wrapper for the jikan API, an unofficial API for MyAnimeList.

## Installation

To get a bug fix or to use a feature from the development version, you can install 
the development version of jikan from GitHub.

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("winstonwhe/jikanr")
```


## Getting help

If you encounter a clear bug, please file an issue with a minimal reproducible example on [GitHub](https://github.com/winstonwhe/jikanr/issues).

---
 Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
  By participating in this project you agree to abide by its terms.
